\cvsection{Experience}

\begin{cventries}
 
  \cventry
    {Software Engineer} % Job title
    {Microsoft, App Center} % Organization
    {Redmond, WA} % Location
    {August 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Engaged in design sessions for a new mobile backend offering (Mobile Backend as a Service, or MBaaS) which would allow developers to store data in the cloud and share it between users. Product is currently in preview.}
      	\item {Built MBaaS modules for App Center's open source SDK. This included implementing CRUD APIs, handling data serialization and deserialization, and building test app functionality in both Android and iOS.}
        \item {Maintained existing analytics engine and data export functionality through large features and while on call. On call duties included engaging with customers directly to resolve their issues as well as standard incident resolution. Responsible for both frontend and backend issues.}
      \end{cvitems}
    }

  \cventry
    {Software Engineering Intern} % Job title
    {Microsoft, App Center} % Organization
    {Redmond, WA} % Location
    {Summer 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{Implemented the serialization of App Center Analytics data for export to Application Insights to attain feature parity with Hockey App (a product similar to App Center that Microsoft acquired and was deprecating). Currently App Center exports roughly 600k logs per minute to Application Insights.}
      	\item{Collaborated with the Application Insights team and PMs familiar with Hockey App to create an export schema that would give customers the smoothest transition into App Center.}
      	\item{Demoed the final product to the App Center team during the final all-hands meeting of my internship.}
      \end{cvitems}
    }

  \cventry
    {NSF Research Experience for Undergrads (REU) Fellow} % Job title
    {New York Institute of Technology} % Organization
    {New York, New York} % Location
    {Summer 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a machine learning model in MATLAB to identify if a given person was driving a car using driver simulation data that had been previously collected by my faculty mentor.}
        \item{Presented the research in final and mid-point talks and gave smaller weekly progress presentations. Based on these talks, I was selected out of my cohort to attend the 2016 Council on Undergraduate Research’s REU Symposium to present my research.}
        \item {First author on a conference paper about machine learning driver identification, published by my mentor and others.}
      \end{cvitems}
    }

  \cventry
    {Open Source Contributor} % Job title
    {Java Immutable Collections} % Organization
    {Frostburg, MD} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a multiset for Java Immutable Collections, which is an open source library of immutable data structures. Expanded functionality for data structures already in the library.}
        \item {Designed and implemented a stress test for all data structures in the library. This supplemented unit tests by testing library functionality with random values, ensuring there weren't edge case bugs that were being overlooked.}
        \item {Migrated the project from SourceForge to GitHub, which included moving prior releases and setting up the project website using GitHub Pages.}
      \end{cvitems}
    }
\end{cventries}
